Let’s Disco – Publishing person-level data as Linked Data.

### 2015-01-08 paper/ESWC 2015 Tutorial/ESWC2015Tutorial.tex
objectives and audience

\subsection{Objectives of the Tutorial}

@@

\subsection{Intended Audiences}
Linked Data experts that are interested in modelling and publishing complex and highly inter-connected data sets as Linked Data.

@@

Thomas Bosch\footnote{\url{http://boschthomas.blogspot.com}} studies information systems, holds a degree in Computer Science (M.Sc.), and is currently a PhD student.
His research topic is all about RDF validation.
More specifically, he investigates how to validate any RDF constraints (formulated by multiple constraint languages) and how to express them generically. 
He held multiple presentations at international conferences and workshops (e.g. WWW, ISWC, DC, Dagstuhl seminars).

>>>>

\subsection{Objectives of the Tutorial} 
The domain-specific origin of Disco increases the difficulties for adopting it by developers who are not familiar with the domain. However, person-level metadata is not restricted to a particular domain and may be an interesting data source for Linked Data developers. Hence, as our main objective, we want to provide assistence for creating such complex Linked Data sets using Disco. Because of the complexity, we especially want to demonstrate how Disco data sets can be connected with information represented using other existing vocabularies that are relevant in that context. Vice verse, we show how these other vocabualries and data represented with such can benefit from the interplay with Disco.

Another objective of the tutorial is to share our experience in developing a RDF vocabulary out of an existing and highly-complex domain-specific data model. We provide insight into the development and engineering process for creating Disco.
Finally, since Disco is already being adopted in the DDI community, we aim to increase the use of Disco in the Linked Data community.

@@

\subsection{Intended Audiences}
The intended audience of this tutorial are Linked Data developers - beginners as well as experts - who are interested in modelling and publishing complex and highly inter-connected data sets as Linked Data. Since the connection with other vocabulaires like QB, DCAT and PROV-O plays a major role in this context, the tutorial is not restricted to participants who are interested in person-level micro data.

@@

Thomas Bosch\footnote{\url{http://boschthomas.blogspot.com}} studied information systems, holds a degree in Computer Science (M.Sc.), and is currently a PhD student.
His research topic is all about RDF validation.
More specifically, he investigates how to validate any RDF constraints (formulated by multiple constraint languages) and how to express them generically. 
He held multiple presentations at international conferences and workshops (e.g. WWW, ISWC, DC, Dagstuhl seminars).
